The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-09-03 paper/Analisis.tex
first paragraph in the introduction. added some references

[Due to the resonant nature of the Lyman alpha line, gas kinematics
play an important role shaping its morphology.]

>>>>

The detection of strong \ly emission lines has become an essential
method in extragalactic astronomy to find distant star-forming
galaxies
\citep{PartridgePeebles,Rhoads00,Gawiser2007,Koehler2007,Ouchi08,Yamada2012,Schenker2012}. The
galaxies detected using this method receive the 
name of \ly emitters (LAEs). A detailed examination of this galaxy
population has diverse implications for galaxy formation, reonization
and the large scale structure of the Universe. Attempts to fully
exploit the physical information included in the \ly line require an
understading of all the physical factor sinvolved in shaping the
line. Due to the resonant nature of this line, these physical factors
include temperature, density and bulk velocity field of the neutral
Hydrogen in the emitting galaxy and its surroundings.
